---
title: "Output"
author: "Solomon Daner"
output: html_document
---

# Hardcoded Data
```{r}
ProductRecommenderData = data.table :: data.table(CustomerID = rep(c(12346L,12347L),each = 10), 
StockCode = c("23167","23165","22969","22501","22720","23154","22722", 
"23298", "22961", "23293", "23245", "22961", "21977", "22952",
"22730","23240","22624","22950","47566","85123A"),
ProductRank = c(1:10), ModelTimeStamp = "2019-06-23 12:14:10")
```

# View Data
```{r}
ProductRecommenderData
```

# Save Function
```{r}
AutoRecommenderUpdate <- function (
  data,
  FeaturedProduct,
  ReplaceProduct = FALSE,
  N = 10,
  EntityColName  = "CustomerID",
  ProductColName = "StockCode",
  Rank = "ProductRank",
  TimeStamp = "ModelTimeStamp") {
  
  # Ensure data is data.table----
  if (!data.table::is.data.table(data)) {
    data <- data.table::as.data.table(data)
  }
  
  # Gather Data to Determine Correct Scenerio----
  CustomersWithFeaturedItem <- data[get(ProductColName) == FeaturedProduct, get(EntityColName)]
  CustomersWithFeaturedItemTable <- data[get(EntityColName) %in% CustomersWithFeaturedItem]
  CustomersWithoutFeaturedItemTable <- data[!(get(EntityColName) %in% CustomersWithFeaturedItem )]
  
  # The Three Possible Scenerios are Listed Below----
  # No Customer Has the Fetured Product Recommended to Them
  # Every Customer Already Has the Fetured Product Recommended to Them
  # Some Customers Have the Fetured Product Recommended to Them
  if (nrow(CustomersWithFeaturedItemTable) == 0) {
    A <- CustomersWithoutFeaturedItemTable
    B <- NULL
  } else if(nrow(CustomersWithoutFeaturedItemTable) == 0) {
    return ("Every Customer has the featured product")
  } else {
    A <- CustomersWithoutFeaturedItemTable
    B <- CustomersWithFeaturedItemTable
  }
  
  # Choose to replace the least likey product with the featured Product----
  if(ReplaceProduct == TRUE) { 
    if(!N %in% unique(A[,get(Rank)])) {
      stop("Rank does not exist in model")
    }
    data.table::set(
      A, 
      i = A[get(Rank) == N, which = TRUE],
      j = eval(ProductColName), 
      value = FeaturedProduct) 
    data <- data.table::rbindlist(
      list(A,B), 
      fill = TRUE)
    data.table::setorderv(
      data, 
      cols = c(eval(EntityColName),
               eval(Rank)))
    return(data)
    
    # Add the featured product to current recommendations----
  } else {
    
    # Test if timestamp should be added----
    if(is.null(TimeStamp)){
      DT <- data.table::data.table(
        V1 = unique(A[,get(EntityColName)]), 
        V2 = FeaturedProduct,
        V3 = 0)
      data.table::setnames(
        x = DT, 
        old = c("V1",
                "V2",
                "V3"),
        new = c(eval(EntityColName),
                eval(ProductColName),
                eval(Rank)))
    } else {
      DT <- data.table::data.table(
        V1 = unique(A[,get(EntityColName)]), 
        V2 = FeaturedProduct,
        V3 = 0, 
        V4 = unique(A[,get(TimeStamp)]))
      data.table::setnames(
        x = DT, 
        old = c("V1",
                "V2",
                "V3",
                "V4"),
        new = c(eval(EntityColName),
                eval(ProductColName),
                eval(Rank),
                eval(TimeStamp)))
    }
    
    # Finalize data prep and return----
    data <- data.table::rbindlist(
      list(DT,A,B), 
      fill = TRUE)
    data.table::setorderv(
      data, 
      cols = c(eval(EntityColName),
               eval(Rank)))
    return(data)
  }
}
```

# Run Function Tests
```{r} 
Test1 = AutoRecommenderUpdate(data = ProductRecommenderData , FeaturedProduct = "00")
Test1
```
The featured item was successfully added to both customers.

```{r}
Test2 = AutoRecommenderUpdate(data = Test1,FeaturedProduct = "00")
Test2
```
We do not want to run this function if every customer already has the product recommended to them.

```{r}
Test3 = AutoRecommenderUpdate(data = ProductRecommenderData ,FeaturedProduct = "23167")
Test3
```
Notice that only the customer without the featured product get a new record. This avoids duplicate products being recommended to the same customer. 

```{r}
Test4 = AutoRecommenderUpdate(data = ProductRecommenderData,FeaturedProduct = "23167",ReplaceProduct = TRUE)
Test4
```
You have the option to replace products of a perticular rank by sepcifying the N argument (I left it blank so N equals 10 by default). This can be useful if you are worried about overloading your servers with too many products or you want to control the amount of products you want to recommend to your customers.

# Conclusion 
Notice that the featured products will always have a default product rank of 0. Hence, this will be the first product customer's see and it facilitates deletion if needed.
